\Title

### 2020-02-13 manuscript/manuscript.tex
Fix typo
Editing Source distributions section

Now we can define the misfit function as the sum between the data misift and
the Tikhonov regularization function:

@@

The choice of a source distribution is not trivial and plays an important role
on the accuracy of the predictions.

>>>>

Now we can define the misfit function as the sum between the data misfit and
the Tikhonov regularization function:

@@

How to choose how many sources will be used and where to locate them are not
trivial decisions and play an important role on the accuracy of the predictions
and the computational resources needed to fit the sources' coefficients.

The chosen distribution of sources should be reproduce the
measured data on the survey points and simultaneously be able to make accurate
predictions of the measured harmonic field on non observed locations.

A high number of sources scattered on the survey region is capable of
reproducing the observed data. Nevertheless, too many sources will make the
Jacobian matrix too large. This could introduce computational problems: like
the inability of storing the matrix on memory or increasing the computational
time needed to fit the sources' coefficients.
On the other hand, using very few sources will undoubtedly reduce the memory
needs and lower the computational time when fitting the sources' coefficients.
Nevertheless, it could be incapable of making accurate predictions and even
reproducing the measured data if the number of sources is too low.
